---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# epierror

<!-- badges: start -->
<!-- badges: end -->

The goal of epierror is to make errors fun for epidemiologists.

## Installation

You can install the development version of epierror from [GitHub](https://github.com/DOH-PXC5303/epierror.git) with:

``` r
# install.packages("devtools")
devtools::install_github("DOH-PXC5303/epierror")
```

## Example

Use epierror::selectquote() to pull a random quote:

```{r select}
library(epierror)

selectquote()

```

You can also print newlines or send to the console with cat:

```{r cat}
cat(selectquote(nline = T))
```

Formatting quotes in HTML for use in Blastula using epierror::selectquote.html():

```{r html}
selectquote.html()

# Include a <br /> tag for a newline:
selectquote.html(nline = T)
```

Finally, quotes can be pulled as a data.frame using epierror::getquotes():

```{r get}
# Select 2 random quotes
getquotes(2)
```
